Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-30 paper.qmd
Added histogram for Figure 8

## To draw the distance distribution
distance_scurve$group <- "1"
distance_scurve_plot <- ggplot(distance_scurve, 
                        aes(x = group, 
                            y = distance)) + 
  geom_quasirandom(
    size = 2, 
    alpha = 0.3
  ) + 
  ylim(0, max(unlist(distance_scurve$distance))+ 0.5) + 
  coord_flip() + 
  geom_hline(yintercept = benchmark_scurve,
     linetype="solid", 
     color = "black", linewidth=0.5, alpha = 0.5) +
  ylab(expression(d^{(2)})) +
  ggtitle("(d)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        plot.title = element_text(size = 12))
```

@@

mse_scurve_b + cell_count_scurve + 
mse_scurve_lwd + 
distance_scurve_plot + plot_layout(ncol=2)
```

>>>>

## To draw the distance distribution
distance_scurve$group <- "1"
distance_scurve_plot <- ggplot(distance_scurve, 
                        aes(x = group, 
                            y = distance)) + 
  geom_quasirandom(
    size = 2, 
    alpha = 0.3
  ) + 
  ylim(0, max(unlist(distance_scurve$distance))+ 0.5) + 
  coord_flip() + 
  geom_hline(yintercept = benchmark_scurve,
     linetype="solid", 
     color = "black", linewidth=0.5, alpha = 0.5) +
  ylab(expression(d^{(2)})) +
  ggtitle("(d)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        plot.title = element_text(size = 12))

# Define bin width and starting point
bin_width <- hb_obj_scurve$centroids$c_x[2]-hb_obj_scurve2$centroids$c_x[1]
start_point <- bin_width/2

# Create bins and calculate the mean value for each bin range
bins <- seq(start_point, max(distance_scurve$distance) + bin_width, 
            by = bin_width)
bin_labels <- bins[-length(bins)] + bin_width / 2  # mean of each bin range

distance_scurve <- distance_scurve |> 
  mutate(bin = cut(distance, breaks = bins, include.lowest = TRUE, labels = bin_labels))

distance_hist <- ggplot(
  distance_scurve, aes(x = distance)) +
    geom_histogram(
      aes(y = after_stat(count) / sum(after_stat(count))), 
      binwidth = bin_width) +
  scale_x_continuous(breaks = bin_labels, labels = round(bin_labels, 3)) +
  ylab("standardized number of edges") +
  xlab(expression(d^{(2)})) +
  ggtitle("(d)") +
  theme(aspect.ratio = 0.75,
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, angle = 90),
        axis.text.x = element_text(size = 12, angle = 90),
        axis.text.y = element_text(size = 12),
        axis.ticks.x = element_line(), 
        plot.title = element_text(size = 12))
```

@@

mse_scurve_b + cell_count_scurve + 
mse_scurve_lwd + 
distance_hist + plot_layout(ncol=2)
```
